### 2012-06-03 pre.tex
back to chapter files, lots of writing
Chapter 2 draft done.

\ex Russian 1sg. imperfect gaps \citep[after][]{Pesetsky1977}: \\
\begin{tabular}{l l l@{}l@{}l@{}l@{}l@{} l}
   & infinitive &   & 1sg. non-past \\
a. & pobedit{j} & * & pobeʒu  & / & * & pobeʒdu  & `conquer'   \\
   & ubedit{j}  & * & ubeʒu   & / & * & ubeʒdu   & `persuade'  \\
b. & tʃudit{j}  & * & tʃuʒu   & / & * & tʃuʒdu & `act oddly'   \\
   & otʃudit{j} & * & natʃuʒu & / & * & natʃuʒdu & `alienate'  \\
\end{tabular}

\noindent
As \citealt{Pesetsky1977} notes, the ill-formedness of the 1sg. non-past forms is shared by verbs related by prefixation. The opposite pattern can be seen in English.

\ex English preterite gaps: \\
\begin{tabular}{l l l@{}l@{}l@{}l@{}l@{}}
   & present  &   & preterite &   &   &           \\
a. & foresee  &   & foresaw   &   &   &           \\
   & sightsee & * & sightsaw  & / & * & sightseed \\
b. & undergo  &   & underwent &   &   &           \\
   & forgo    & * & forwent   & / & * & forgoed   \\
\end{tabular}

>>>>

\begin{example}[Russian 1sg. imperfect gaps (after \citealp{Pesetsky1977})]
\begin{tabular}{l l l@{}l@{}l@{}l@{}l@{} l}
   & infinitive &   & 1sg. non-past \\
a. & pobedit{j} & * & pobeʒu  & / & * & pobeʒdu  & `conquer'   \\
   & ubedit{j}  & * & ubeʒu   & / & * & ubeʒdu   & `persuade'  \\
b. & tʃudit{j}  & * & tʃuʒu   & / & * & tʃuʒdu & `act oddly'   \\
   & naʃudit{j} & * & natʃuʒu & / & * & natʃuʒdu & `alienate'  \\
\end{tabular}
\end{example}

\noindent As \citeauthor{Pesetsky1977} notes, the ill-formedness of the 1sg. non-past forms is shared by verbs related by prefixation. The opposite pattern can be seen in English.

\begin{example}[English preterite gaps]
\begin{tabular}{l l l@{}l@{}l@{}l@{}l@{}}
   & present  &   & preterite                     \\
a. & foresee  &   & foresaw   &   &   &           \\
   & sightsee & * & sightsaw  & / & * & sightseed \\
b. & undergo  &   & underwent &   &   &           \\
   & forgo    & * & forwent   & / & * & forgoed   \\
\end{tabular}
\end{example}
